---
title: "Student grouping by Tabu Search"
output: html_document
---

This vignette describes how to run the genetic algorithm code given a student survey. The algorithm implemented and used in this vignette was taken from the following article: `http://ieeexplore.ieee.org/document/5518761/`

```{r, message=FALSE, warning=FALSE}
root = paste0(getwd()) #root = 
#load the functions
source(paste0(root, "/code/ga.r"))

```


```{r}
#read the input file
tab = read.table(paste0(root, '/example/simple-survey.csv'), sep=',')
group_size = 6
total_student = nrow(tab) - 1
# print survey results
head(tab)
```


Before running the algorithm, I am parsing `simple-survey.csv` file for student feedback. The input is then updated into a list of matrices where each matrix contains `student-skill-level` of size `student_countXskill_count`. Please change the following code block and the definition of `arrange_skills` function according to your input file. 
```{r}
# read the 2nd column for skills on various subjects
skills_knowledge = as.character(tab[-1,2]); 

# read the 2nd column for social skills
social_skills = as.character(tab[-1,4])

skills = arrange_skills(total_student, skills_knowledge, social_skills)
```


Run the k-nary-tabu search algorithm. the algorithm takes considerable amount of time to run and the algorithm writes the group configuration in `group_configuration.txt` file. For new survey, run the following code fragment to generate `group_configuration.txt` file for next stages.
```{r, eval=FALSE}
config = k_nary_tabu(total_student, grpsize, eval_maximally_diverse_config, skills)
```


I am reading previously generated group configuration file: `group_configuration.txt`.
```{r, message=FALSE, warning=FALSE, eval=FALSE}
config = read.table('group_configuration.txt')
```

Outputting the group results and checking the grouping quality.
```{r, message=FALSE, warning=FALSE, eval=FALSE}
ncls = 56; grpsize = 4

skills = read_skills(ncls)
grps = eval_grouping(config, 'subjects'); grps
grps = eval_grouping(config, 'socials'); grps
eval_config2(config$V1, skills)

```
